### 2023-10-20 main.tex
initial

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{\textbf{An Investigation into Quantitatively Predicting Reading Preferences}} % Title of the assignment

\author{Math AI HL - Rahma Ammiche} % Author name and email address

\date{Words: ???} % University, school and/or department name(s) and a date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{Introduction} % Unnumbered section

Waffle, waffle, waffle. dgdgd

% Math equation/formula
\begin{equation}
	I = \int_{a}^{b} f(x) \; \text{d}x.
\end{equation}

Anddddd surprise! More waffle. Just with a cheeky equation to spice things up.

\begin{info}[Reflection:] % Information block
	Waffle about my sins and wrongdoings. 
\end{info}

\subsection{Aims}
If any.

\subsection{Rationale}
Here I attempt to explain the absolutely unreasonable reasons for which I would want to carry out an investigation like this.

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Problem title} % Numbered section

In hac habitasse platea dictumst. Curabitur mattis elit sit amet justo luctus vestibulum. In hac habitasse platea dictumst. Pellentesque lobortis justo enim, a condimentum massa tempor eu. Ut quis nulla a quam pretium eleifend nec eu nisl. Nam cursus porttitor eros, sed luctus ligula convallis quis. Nam convallis, ligula in auctor euismod, ligula mauris fringilla tellus, et egestas mauris odio eget diam. Praesent sodales in ipsum eu dictum.

%------------------------------------------------

\subsection{Theoretical viewpoint}

Maecenas consectetur metus at tellus finibus condimentum. Proin arcu lectus, ultrices non tincidunt et, tincidunt ut quam. Integer luctus posuere est, non maximus ante dignissim quis. Nunc a cursus erat. Curabitur suscipit nibh in tincidunt sagittis. Nam malesuada vestibulum quam id gravida. Proin ut dapibus velit. Vestibulum eget quam quis ipsum semper convallis. Duis consectetur nibh ac diam dignissim, id condimentum enim dictum. Nam aliquet ligula eu magna pellentesque, nec sagittis leo lobortis. Aenean tincidunt dignissim egestas. Morbi efficitur risus ante, id tincidunt odio pulvinar vitae.

Curabitur tempus hendrerit nulla. Donec faucibus lobortis nibh pharetra sagittis. Sed magna sem, posuere eget sem vitae, finibus consequat libero. Cras aliquet sagittis erat ut semper. Aenean vel enim ipsum. Fusce ut felis at eros sagittis bibendum mollis lobortis libero. Donec laoreet nisl vel risus lacinia elementum non nec lacus. Nullam luctus, nulla volutpat ultricies ultrices, quam massa placerat augue, ut fringilla urna lectus nec nibh. Vestibulum efficitur condimentum orci a semper. Pellentesque ut metus pretium lacus maximus semper. Sed tellus augue, consectetur rhoncus eleifend vel, imperdiet nec turpis. Nulla ligula ante, malesuada quis orci a, ultricies blandit elit.

% Numbered question, with subquestions in an enumerate environment
\begin{question}
	Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit amet, consectetuer adipiscing elit.

	% Subquestions numbered with letters
	\begin{enumerate}[(a)]
		\item Do this.
		\item Do that.
		\item Do something else.
	\end{enumerate}
\end{question}

%------------------------------------------------

\subsection{Algorithmic issues}

In malesuada ullamcorper urna, sed dapibus diam sollicitudin non. Donec elit odio, accumsan ac nisl a, tempor imperdiet eros. Donec porta tortor eu risus consequat, a pharetra tortor tristique. Morbi sit amet laoreet erat. Morbi et luctus diam, quis porta ipsum. Quisque libero dolor, suscipit id facilisis eget, sodales volutpat dolor. Nullam vulputate interdum aliquam. Mauris id convallis erat, ut vehicula neque. Sed auctor nibh et elit fringilla, nec ultricies dui sollicitudin. Vestibulum vestibulum luctus metus venenatis facilisis. Suspendisse iaculis augue at vehicula ornare. Sed vel eros ut velit fermentum porttitor sed sed massa. Fusce venenatis, metus a rutrum sagittis, enim ex maximus velit, id semper nisi velit eu purus.

\begin{center}
	\begin{minipage}{0.5\linewidth} % Adjust the minipage width to accomodate for the length of algorithm lines
		\begin{algorithm}[H]
			\KwIn{$(a, b)$, two floating-point numbers}  % Algorithm inputs
			\KwResult{$(c, d)$, such that $a+b = c + d$} % Algorithm outputs/results
			\medskip
			\If{$\vert b\vert > \vert a\vert$}{
				exchange $a$ and $b$ \;
			}
			$c \leftarrow a + b$ \;
			$z \leftarrow c - a$ \;
			$d \leftarrow b - z$ \;
			{\bf return} $(c,d)$ \;
			\caption{\texttt{FastTwoSum}} % Algorithm name
			\label{alg:fastTwoSum}   % optional label to refer to
		\end{algorithm}
	\end{minipage}
\end{center}

Fusce varius orci ac magna dapibus porttitor. In tempor leo a neque bibendum sollicitudin. Nulla pretium fermentum nisi, eget sodales magna facilisis eu. Praesent aliquet nulla ut bibendum lacinia. Donec vel mauris vulputate, commodo ligula ut, egestas orci. Suspendisse commodo odio sed hendrerit lobortis. Donec finibus eros erat, vel ornare enim mattis et.

% Numbered question, with an optional title
\begin{question}[\itshape (with optional title)]
	In congue risus leo, in gravida enim viverra id. Donec eros mauris, bibendum vel dui at, tempor commodo augue. In vel lobortis lacus. Nam ornare ullamcorper mauris vel molestie. Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel. Nam pulvinar justo nec neque egestas tristique. Donec ac dolor at libero congue varius sed vitae lectus. Donec et tristique nulla, sit amet scelerisque orci. Maecenas a vestibulum lectus, vitae gravida nulla. Proin eget volutpat orci. Morbi eu aliquet turpis. Vivamus molestie urna quis tempor tristique. Proin hendrerit sem nec tempor sollicitudin.
\end{question}

Mauris interdum porttitor fringilla. Proin tincidunt sodales leo at ornare. Donec tempus magna non mauris gravida luctus. Cras vitae arcu vitae mauris eleifend scelerisque. Nam sem sapien, vulputate nec felis eu, blandit convallis risus. Pellentesque sollicitudin venenatis tincidunt. In et ipsum libero. Nullam tempor ligula a massa convallis pellentesque.

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------

\section{Implementation}

Proin lobortis efficitur dictum. Pellentesque vitae pharetra eros, quis dignissim magna. Sed tellus leo, semper non vestibulum vel, tincidunt eu mi. Aenean pretium ut velit sed facilisis. Ut placerat urna facilisis dolor suscipit vehicula. Ut ut auctor nunc. Nulla non massa eros. Proin rhoncus arcu odio, eu lobortis metus sollicitudin eu. Duis maximus ex dui, id bibendum diam dignissim id. Aliquam quis lorem lorem. Phasellus sagittis aliquet dolor, vulputate cursus dolor convallis vel. Suspendisse eu tellus feugiat, bibendum lectus quis, fermentum nunc. Nunc euismod condimentum magna nec bibendum. Curabitur elementum nibh eu sem cursus, eu aliquam leo rutrum. Sed bibendum augue sit amet pharetra ullamcorper. Aenean congue sit amet tortor vitae feugiat.

In congue risus leo, in gravida enim viverra id. Donec eros mauris, bibendum vel dui at, tempor commodo augue. In vel lobortis lacus. Nam ornare ullamcorper mauris vel molestie. Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel. Nam pulvinar justo nec neque egestas tristique. Donec ac dolor at libero congue varius sed vitae lectus. Donec et tristique nulla, sit amet scelerisque orci. Maecenas a vestibulum lectus, vitae gravida nulla. Proin eget volutpat orci. Morbi eu aliquet turpis. Vivamus molestie urna quis tempor tristique. Proin hendrerit sem nec tempor sollicitudin.

% File contents
\begin{file}[hello.py]
\begin{lstlisting}[language=Python]
#! /usr/bin/python

import sys
sys.stdout.write("Hello World!\n")
\end{lstlisting}
\end{file}

Fusce eleifend porttitor arcu, id accumsan elit pharetra eget. Mauris luctus velit sit amet est sodales rhoncus. Donec cursus suscipit justo, sed tristique ipsum fermentum nec. Ut tortor ex, ullamcorper varius congue in, efficitur a tellus. Vivamus ut rutrum nisi. Phasellus sit amet enim efficitur, aliquam nulla id, lacinia mauris. Quisque viverra libero ac magna maximus efficitur. Interdum et malesuada fames ac ante ipsum primis in faucibus. Vestibulum mollis eros in tellus fermentum, vitae tristique justo finibus. Sed quis vehicula nibh. Etiam nulla justo, pellentesque id sapien at, semper aliquam arcu. Integer at commodo arcu. Quisque dapibus ut lacus eget vulputate.

% Command-line "screenshot"
\begin{commandline}
	\begin{verbatim}
		$ chmod +x hello.py
		$ ./hello.py

		Hello World!
	\end{verbatim}
\end{commandline}

Vestibulum sodales orci a nisi interdum tristique. In dictum vehicula dui, eget bibendum purus elementum eu. Pellentesque lobortis mattis mauris, non feugiat dolor vulputate a. Cras porttitor dapibus lacus at pulvinar. Praesent eu nunc et libero porttitor malesuada tempus quis massa. Aenean cursus ipsum a velit ultricies sagittis. Sed non leo ullamcorper, suscipit massa ut, pulvinar erat. Aliquam erat volutpat. Nulla non lacus vitae mi placerat tincidunt et ac diam. Aliquam tincidunt augue sem, ut vestibulum est volutpat eget. Suspendisse potenti. Integer condimentum, risus nec maximus elementum, lacus purus porta arcu, at ultrices diam nisl eget urna. Curabitur sollicitudin diam quis sollicitudin varius. Ut porta erat ornare laoreet euismod. In tincidunt purus dui, nec egestas dui convallis non. In vestibulum ipsum in dictum scelerisque.

% Warning text, with a custom title
\begin{warn}[Notice:]
  In congue risus leo, in gravida enim viverra id. Donec eros mauris, bibendum vel dui at, tempor commodo augue. In vel lobortis lacus. Nam ornare ullamcorper mauris vel molestie. Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel. Nam pulvinar justo nec neque egestas tristique. Donec ac dolor at libero congue varius sed vitae lectus. Donec et tristique nulla, sit amet scelerisque orci. Maecenas a vestibulum lectus, vitae gravida nulla. Proin eget volutpat orci. Morbi eu aliquet turpis. Vivamus molestie urna quis tempor tristique. Proin hendrerit sem nec tempor sollicitudin.
\end{warn}

%----------------------------------------------------------------------------------------

\end{document}

### 2023-10-20 main.tex
.

@@
 
-\documentclass{article}
-
+\documentclass[12pt]{article}
+\usepackage{setspace}
 \input{structure.tex} % Include the file specifying the document structure and custom commands
@@
 
-\title{\textbf{An Investigation into Quantitatively Predicting Reading Preferences}} % Title of the assignment
+\title{\textbf{Comparing and Analyzing the Effectiveness of Various String Matching Algorithms Across Different Domains}} % Title of the assignment
 
-\author{Math AI HL - Rahma Ammiche} % Author name and email address
+\author{\textbf{Research Question -} How do different string \and matching algorithms perform across various application domains, \and and what factors contribute to their varying effectiveness?} % Author name and email address
 
-\date{Words: ???} % University, school and/or department name(s) and a date
+\date{\textbf{Words}: not enough} % University, school and/or department name(s) and a date
 
@@
 
+\doublespacing
+
 \maketitle % Print the title
+\thispagestyle{empty}
+\pagebreak
+\tableofcontents
+\thispagestyle{empty}
 
-%----------------------------------------------------------------------------------------
-%	INTRODUCTION
-%----------------------------------------------------------------------------------------
+\clearpage
+\pagenumbering{arabic}
 
+\pagebreak
 \section{Introduction} % Unnumbered section
 
-Waffle, waffle, waffle. dgdgd
+The impacts and applications of string matching algorithms extend far beyond their immediate textual applications; its quotidian use in domains such as bioinformatics, web crawling and security systems make it a pertinent area of study within computer science.
+There is also constant research being carried out to identify more efficient algorithms, and find ways in which to combine them with other disciplines to carry out certain tasks.
 
-% Math equation/formula
-\begin{equation}
-	I = \int_{a}^{b} f(x) \; \text{d}x.
-\end{equation}
+For instance, multiple studies have been recently published performing various comparative analyses of new string matching algorithms [5], and their applicability to a wide range of domains such as biological sequences [6], quantum computing [7], and instrusion detection systems [8].
+These findings indicate the modern-day relevance and applicability of string matching algorithms and demonstrate its worthiness as a subject of investigation.
 
-Anddddd surprise! More waffle. Just with a cheeky equation to spice things up.
+Similarly, this paper seeks to adopt an investigative style by examining \textbf{how different string matching algorithms perform across various application domains, and the factors that contribute to their varying effectiveness}.
+The choice of this research question is both relevant and justifiable, reflecting the persistent demand for evaluating and optimizing string matching algorithms across a range of applications.
 
-\begin{info}[Reflection:] % Information block
-	Waffle about my sins and wrongdoings. 
-\end{info}
+To examine this subject, three popular string matching algorithms were programmed and tested on their ability to carry out three tasks from three different domains.
+They are then evaluated on their efficiency, and applicability.
+To maintain focus on the research question, the reasoning and rationale behind all the decisions will be explained to demonstrate how they directly address the question.
 
-\subsection{Aims}
-If any.
+\section{Theoretical Background} % Numbered section
 
-\subsection{Rationale}
-Here I attempt to explain the absolutely unreasonable reasons for which I would want to carry out an investigation like this.
+\subsection{Topic Overview}
 
-%----------------------------------------------------------------------------------------
-%	PROBLEM 1
-%----------------------------------------------------------------------------------------
+\subsection{Naive Algorithm}
 
-\section{Problem title} % Numbered section
+\subsection{Knuth-Morris-Pratt Algorithm}
 
-In hac habitasse platea dictumst.
-Curabitur mattis elit sit amet justo luctus vestibulum.
-In hac habitasse platea dictumst.
-Pellentesque lobortis justo enim, a condimentum massa tempor eu.
-Ut quis nulla a quam pretium eleifend nec eu nisl.
-Nam cursus porttitor eros, sed luctus ligula convallis quis.
-Nam convallis, ligula in auctor euismod, ligula mauris fringilla tellus, et egestas mauris odio eget diam.
-Praesent sodales in ipsum eu dictum.
+\subsection{Rabin-Karp Algorithm}
 
-%------------------------------------------------
+\section{Experimental Methodology}
 
-\subsection{Theoretical viewpoint}
+\subsection{Research Question Decomposition}
+
+\subsection{Measuring Performance}
+
+\subsection{Application to Domains}
+
+\section{Experimental Results Analysis}
+
+\section{Conclusion}
+
+\section{References}
 

### 2023-10-20 main.tex
halfway updated

@@
 \documentclass[12pt]{article}
-\usepackage{setspace}
+
 \input{structure.tex} % Include the file specifying the document structure and custom commands
@@
 \section{Theoretical Background} % Numbered section
+\subsection{Topic Overview}
+String matching algorithms (often used interchangeably with string or pattern searching
+algorithms) are a subset of string algorithms. The term is composed of three parts:
+“string”, “matching”, and “algorithm”. Strings refer to an abstract data type consisting
+1
+of a sequence of characters. Matching relates to it's function to identify specific patterns
+within a larger dataset that match a criteria. As for algorithms, these can be defined as a set of instructions designed to carry out a function. These algorithms take in two
+inputs: a pattern ($P$), which is a sequence of characters being searched for within a larger
+sequence, a text ($T$). Within string matching problems, there exists two general variants
+[2]:
 
-\subsection{Topic Overview}
+\begin{enumerate}
+	\item \textbf{Find occurences of a pre-defined pattern in a previously unseen dataset} \\
+	Carried out using finite automata models [4] (an idealized machine used to recognize
+	patterns in a given text; it accepts or rejects the input depending on whether the
+	pre-defined pattern occurs in the text) or through the combinatorial properties of
+	strings.
+	\item \textbf{Find occurences of any identifiable patterns in a given text} \\
+	Carried out using finite automata and binary trees.
+\end{enumerate}
+
+Linking into the mentioned problem variants, these algorithms can be further classified into two categories [1]: exact, and approximate string matching algorithms. As
+its name suggests, the former refers to finding occurences of a pattern that match it to
+the character, whereas the latter allows for some variation or deviation. For the purpose
+of this investigation, the first problem variant, as well as an exact-string matching approach was chosen for all the algorithms, both for simplicity and control. Three exact
+string matching algorithms were chosen for comparison based on their popularity: Naive,
+Knuth-Morris-Pratt, and Rabin-Karp. Prior to their explanations, it is important to note
+that the following notation will be used:
+
+\begin{table}[htbp]\caption{String Matching Algorithm Notation}
+\begin{center}% used the environment to augment the vertical space
+% between the caption and the table
+\begin{tabular}{r c p{10cm} }
+\toprule
+$m$ & $=$ & Length of $P$\\
+$n$ & $=$ & Length of $T$\\
+$T_{j}$ & : & For an input text $T$ where $0 \le j \le n - 1$\\
+$P_{i}$ & : & For an input pattern $P$ where $0 \le i \le m - 1$\\
+\bottomrule
+\end{tabular}
+\end{center}
+\label{tab:StringMatchinAlgorithmNotation}
+\end{table}
 
@@
 
+[9] Also known as the “brute-force” approach, this algorithm compares the first indexes
+of both $P$ and $T$. If $P_{i}$ equals $T_{j}$ then $i$ and $j$ are incremented and further compared. If
+$P_{i}$ reaches $m - 1$ then a variable containing the number of occurences of $P$ is incremented
+and $P_{i}$ is reset to $P_{i=0}$. On the other hand, if they do not match, then $P_{i}$ is reset and
+$j$ incremented. This repeats until $T_{j=m-1}$ is reached. Since there is no pre-processing
+phase, the only time complexity taken into account is during its matching phase, which
+is expected to be $O(n \cdot m)$ [10]. The algorithm is better expressed in pseudocode:
+
+\begin{center}
+\begin{singlespace}
+\begin{minipage}{0.75\linewidth}
+\begin{algorithm}[H]
+	$n \leftarrow T.length()$ \;
+	$m \leftarrow P.length()$ \;
+	\For{$i \leftarrow 0$ \bf{to} $n-m$}{
+		\While{$j < m$ \bf{and} $P[j] == T[i+j]$}{
+			$j \leftarrow j + 1$}
+		\If{$j == m$}{
+			\textbf{output} "Pattern found at index" + $i$}
+	}
+	\caption{Naive}
+\end{algorithm}
+\end{minipage}
+\end{singlespace}
+\end{center}
+
+The best case scenario of this process is when $P_{i=0}$ is not present in $T$, yielding an
+$O(n)$ number of comparisons, making it particularly advantageous for solving problems
+with small $n$ and $m$ values. When larger sets are used however, the algorithm's efficiency significantly deteriorates. The worst case scenario for instance would be when
+all the characters for $P$ and $T$ are the same (${P_{i=0} \ldots P_{m-1}} = {T_{j=0} \ldots T_{n-1}}$) or
+when all the characters for both $P$ and $T$ are the same except for their last characters ($({P_{i=0} \ldots P_{m-2}} = {T_{j=0} \ldots T_{n-2}}) \land (P_{m-1} = T_{n-1})$). This would yield an
+$O(m \cdot (n - m + 1))$ number of comparisons.
+
 \subsection{Knuth-Morris-Pratt Algorithm}
+
+[10] [11] This algorithm differs from the Naive approach by implementing an LPS table
+as part of the pre-processing phase. Its purpose is to keep track of the comparisons made;
+after a mismatch, it is used to calculate where to begin the next match without needing
+to reset $P$. The table is constructed by determining the largest prefix of $P$ that matches
+its largest suffix -- the main idea is to identify how many characters can be skipped, by not
+matching characters that have already been calculated to match (eliminating redundancy).
+Although appearing complicated, this can be better explained through pseudocode and a
+practical example represented through a truth table. Upon initalization, the LPS table is
+an array of 0s of length $m$. For demonstration purposes, $P$ will equal "$ABABA$":
+
+\begin{table}[!htbp]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+        \hline
+        Index ($i$) & Pattern Character ($P_{i}$) & Length (of Suffix-Prefix match) & LPS Value ($LPS[i]$) \\
+        \hline
+        0 & A & 0 & 0 \\
+        1 & B & 0 & 0 \\
+        2 & A & 0 & 1 \\
+        3 & B & 1 & 2 \\
+        4 & A & 2 & 3 \\
+        \hline
+    \end{tabular}
+    \caption{Truth Table for Pattern "ABABA"}
+\end{table}
+
+\begin{center}
+	\begin{singlespace}
+	\begin{minipage}{0.75\linewidth}
+	\begin{algorithm}[H]
+		$length \leftarrow 0$ \;
+		$LPS \leftarrow m * [0]$ \;
+		\While{$i < m$}{
+			\If{$P[i] == P[m]$}{
+				$length \leftarrow length + 1$\;
+				$LPS[i] \leftarrow 0$\;
+				$i \leftarrow i + 1$\;
+			}
+			\ElseIf{$length \neq 0$}{
+				$length \leftarrow LPS[length - 1]$\;
+			}
+			\Else{
+				$LPS[i] \leftarrow 0$\;
+				$i \leftarrow i + 1$\;
+			}
+		}
+		\textbf{return} $LPS$
+		\caption{CalculateLPSArray}
+	\end{algorithm}
+	\end{minipage}
+	\end{singlespace}
+	\end{center}
 
@@
 \section{References}
-
-Maecenas consectetur metus at tellus finibus condimentum.
-Proin arcu lectus, ultrices non tincidunt et, tincidunt ut quam.
-Integer luctus posuere est, non maximus ante dignissim quis.
-Nunc a cursus erat.
-Curabitur suscipit nibh in tincidunt sagittis.
-Nam malesuada vestibulum quam id gravida.
-Proin ut dapibus velit.
-Vestibulum eget quam quis ipsum semper convallis.
-Duis consectetur nibh ac diam dignissim, id condimentum enim dictum.
-Nam aliquet ligula eu magna pellentesque, nec sagittis leo lobortis.
-Aenean tincidunt dignissim egestas.
-Morbi efficitur risus ante, id tincidunt odio pulvinar vitae.
-
-Curabitur tempus hendrerit nulla.
-Donec faucibus lobortis nibh pharetra sagittis.
-Sed magna sem, posuere eget sem vitae, finibus consequat libero.
-Cras aliquet sagittis erat ut semper.
-Aenean vel enim ipsum.
-Fusce ut felis at eros sagittis bibendum mollis lobortis libero.
-Donec laoreet nisl vel risus lacinia elementum non nec lacus.
-Nullam luctus, nulla volutpat ultricies ultrices, quam massa placerat augue, ut fringilla urna lectus nec nibh.
-Vestibulum efficitur condimentum orci a semper.
-Pellentesque ut metus pretium lacus maximus semper.
-Sed tellus augue, consectetur rhoncus eleifend vel, imperdiet nec turpis.
-Nulla ligula ante, malesuada quis orci a, ultricies blandit elit.
-
-% Numbered question, with subquestions in an enumerate environment
-\begin{question}
-	Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-
-	% Subquestions numbered with letters
-	\begin{enumerate}[(a)]
-		\item Do this.
-		\item Do that.
-		\item Do something else.
-	\end{enumerate}
-\end{question}
-
-%------------------------------------------------
-
-\subsection{Algorithmic issues}
-
-In malesuada ullamcorper urna, sed dapibus diam sollicitudin non.
-Donec elit odio, accumsan ac nisl a, tempor imperdiet eros.
-Donec porta tortor eu risus consequat, a pharetra tortor tristique.
-Morbi sit amet laoreet erat.
-Morbi et luctus diam, quis porta ipsum.
-Quisque libero dolor, suscipit id facilisis eget, sodales volutpat dolor.
-Nullam vulputate interdum aliquam.
-Mauris id convallis erat, ut vehicula neque.
-Sed auctor nibh et elit fringilla, nec ultricies dui sollicitudin.
-Vestibulum vestibulum luctus metus venenatis facilisis.
-Suspendisse iaculis augue at vehicula ornare.
-Sed vel eros ut velit fermentum porttitor sed sed massa.
-Fusce venenatis, metus a rutrum sagittis, enim ex maximus velit, id semper nisi velit eu purus.
-
-\begin{center}
-	\begin{minipage}{0.5\linewidth} % Adjust the minipage width to accomodate for the length of algorithm lines
-		\begin{algorithm}[H]
-			\KwIn{$(a, b)$, two floating-point numbers}  % Algorithm inputs
-			\KwResult{$(c, d)$, such that $a+b = c + d$} % Algorithm outputs/results
-			\medskip
-			\If{$\vert b\vert > \vert a\vert$}{
-				exchange $a$ and $b$ \;
-			}
-			$c \leftarrow a + b$ \;
-			$z \leftarrow c - a$ \;
-			$d \leftarrow b - z$ \;
-			{\bf return} $(c,d)$ \;
-			\caption{\texttt{FastTwoSum}} % Algorithm name
-			\label{alg:fastTwoSum}   % optional label to refer to
-		\end{algorithm}
-	\end{minipage}
-\end{center}
-
-Fusce varius orci ac magna dapibus porttitor.
-In tempor leo a neque bibendum sollicitudin.
-Nulla pretium fermentum nisi, eget sodales magna facilisis eu.
-Praesent aliquet nulla ut bibendum lacinia.
-Donec vel mauris vulputate, commodo ligula ut, egestas orci.
-Suspendisse commodo odio sed hendrerit lobortis.
-Donec finibus eros erat, vel ornare enim mattis et.
 
@@
 
-Mauris interdum porttitor fringilla.
-Proin tincidunt sodales leo at ornare.
-Donec tempus magna non mauris gravida luctus.
-Cras vitae arcu vitae mauris eleifend scelerisque.
-Nam sem sapien, vulputate nec felis eu, blandit convallis risus.
-Pellentesque sollicitudin venenatis tincidunt.
-In et ipsum libero.
-Nullam tempor ligula a massa convallis pellentesque.
-
-%----------------------------------------------------------------------------------------
-%	PROBLEM 2
-%----------------------------------------------------------------------------------------
-
-\section{Implementation}
-
-Proin lobortis efficitur dictum.
-Pellentesque vitae pharetra eros, quis dignissim magna.
-Sed tellus leo, semper non vestibulum vel, tincidunt eu mi.
-Aenean pretium ut velit sed facilisis.
-Ut placerat urna facilisis dolor suscipit vehicula.
-Ut ut auctor nunc.
-Nulla non massa eros.
-Proin rhoncus arcu odio, eu lobortis metus sollicitudin eu.
-Duis maximus ex dui, id bibendum diam dignissim id.
-Aliquam quis lorem lorem.
-Phasellus sagittis aliquet dolor, vulputate cursus dolor convallis vel.
-Suspendisse eu tellus feugiat, bibendum lectus quis, fermentum nunc.
-Nunc euismod condimentum magna nec bibendum.
-Curabitur elementum nibh eu sem cursus, eu aliquam leo rutrum.
-Sed bibendum augue sit amet pharetra ullamcorper.
-Aenean congue sit amet tortor vitae feugiat.
-
-In congue risus leo, in gravida enim viverra id.
-Donec eros mauris, bibendum vel dui at, tempor commodo augue.
-In vel lobortis lacus.
-Nam ornare ullamcorper mauris vel molestie.
-Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel.
-Nam pulvinar justo nec neque egestas tristique.
-Donec ac dolor at libero congue varius sed vitae lectus.
-Donec et tristique nulla, sit amet scelerisque orci.
-Maecenas a vestibulum lectus, vitae gravida nulla.
-Proin eget volutpat orci.
-Morbi eu aliquet turpis.
-Vivamus molestie urna quis tempor tristique.
-Proin hendrerit sem nec tempor sollicitudin.
-
-% File contents
-\begin{file}[hello.py]
-\begin{lstlisting}[language=Python]
-#! /usr/bin/python
-
-import sys
-sys.stdout.write("Hello World!\n")
-\end{lstlisting}
-\end{file}
-
-Fusce eleifend porttitor arcu, id accumsan elit pharetra eget.
-Mauris luctus velit sit amet est sodales rhoncus.
-Donec cursus suscipit justo, sed tristique ipsum fermentum nec.
-Ut tortor ex, ullamcorper varius congue in, efficitur a tellus.
-Vivamus ut rutrum nisi.
-Phasellus sit amet enim efficitur, aliquam nulla id, lacinia mauris.
-Quisque viverra libero ac magna maximus efficitur.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Vestibulum mollis eros in tellus fermentum, vitae tristique justo finibus.
-Sed quis vehicula nibh.
-Etiam nulla justo, pellentesque id sapien at, semper aliquam arcu.
-Integer at commodo arcu.
-Quisque dapibus ut lacus eget vulputate.
-
-% Command-line "screenshot"
-\begin{commandline}
-	\begin{verbatim}
-		$ chmod +x hello.py
-		$ ./hello.py
-
-		Hello World!
-	\end{verbatim}
-\end{commandline}
-
-Vestibulum sodales orci a nisi interdum tristique.
-In dictum vehicula dui, eget bibendum purus elementum eu.
-Pellentesque lobortis mattis mauris, non feugiat dolor vulputate a.
-Cras porttitor dapibus lacus at pulvinar.
-Praesent eu nunc et libero porttitor malesuada tempus quis massa.
-Aenean cursus ipsum a velit ultricies sagittis.
-Sed non leo ullamcorper, suscipit massa ut, pulvinar erat.
-Aliquam erat volutpat.
-Nulla non lacus vitae mi placerat tincidunt et ac diam.
-Aliquam tincidunt augue sem, ut vestibulum est volutpat eget.
-Suspendisse potenti.
-Integer condimentum, risus nec maximus elementum, lacus purus porta arcu, at ultrices diam nisl eget urna.
-Curabitur sollicitudin diam quis sollicitudin varius.
-Ut porta erat ornare laoreet euismod.
-In tincidunt purus dui, nec egestas dui convallis non.
-In vestibulum ipsum in dictum scelerisque.
-
-% Warning text, with a custom title
-\begin{warn}[Notice:]
-  In congue risus leo, in gravida enim viverra id.
-Donec eros mauris, bibendum vel dui at, tempor commodo augue.
-In vel lobortis lacus.
-Nam ornare ullamcorper mauris vel molestie.
-Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel.
-Nam pulvinar justo nec neque egestas tristique.
-Donec ac dolor at libero congue varius sed vitae lectus.
-Donec et tristique nulla, sit amet scelerisque orci.
-Maecenas a vestibulum lectus, vitae gravida nulla.
-Proin eget volutpat orci.
-Morbi eu aliquet turpis.
-Vivamus molestie urna quis tempor tristique.
-Proin hendrerit sem nec tempor sollicitudin.
-\end{warn}
-
-%----------------------------------------------------------------------------------------
-
 \end{document}

### 2023-10-20 main.tex
werwwdsgsfffds

@@
 
+Afterwards, the main phase involves applying the calculated LPS table on $T$. The
+indexes $i$ and $j$ both begin at 0, and are incremented while $P_{i}$ matches $T_{j}$. When a
+mismatch occurs, it becomes apparent that the characters in $P$ match with the characters
+of $T$ up to the mismatch ($P_{0 \ldots (i-1)} = T_{j-i \ldots j-1}$). Moreover, from the LPS table, it is known
+that $LPS[i - 1]$ represents the length of the longest part of the prefix and suffix of $P$.
+With these pieces of information, it can be concluded that the characters in $P_{0 \ldots i-1}$ do
+not need to be checked with $T_{j-i \ldots j-1}$ since it is already known that they match. Thus,
+these can be skipped in both $P$ and $T$. The exact process is presented in pseudocode here
+below:
+
+\begin{center}
+\begin{singlespace}
+\begin{minipage}{0.75\linewidth}
+\begin{algorithm}[H]
+	$length \leftarrow 0$ \;
+	$LPS \leftarrow m * [0]$ \;
+	\While{$i < m$}{
+		\If{$P[i] == P[m]$}{
+			$length \leftarrow length + 1$\;
+			$LPS[i] \leftarrow 0$\;
+			$i \leftarrow i + 1$\;
+		}
+		\ElseIf{$length \neq 0$}{
+			$length \leftarrow LPS[length - 1]$\;
+		}
+		\Else{
+			$LPS[i] \leftarrow 0$\;
+			$i \leftarrow i + 1$\;
+		}
+	}
+	\textbf{return} $LPS$
+	\caption{CalculateLPSArray}
+\end{algorithm}
+\end{minipage}
+\end{singlespace}
+\end{center}
+
 \subsection{Rabin-Karp Algorithm}

### 2023-10-21 main.tex
finished reformatting

@@
 	$m \leftarrow P.length()$ \;
+
+	\bigskip
+
 	\For{$i \leftarrow 0$ \bf{to} $n-m$}{
@@
 	$LPS \leftarrow m * [0]$ \;
+
+	\bigskip
+
 	\While{$i < m$}{
@@
 	}
+
 	\textbf{return} $LPS$
@@
 \begin{algorithm}[H]
-	$length \leftarrow 0$ \;
-	$LPS \leftarrow m * [0]$ \;
-	\While{$i < m$}{
-		\If{$P[i] == P[m]$}{
-			$length \leftarrow length + 1$\;
-			$LPS[i] \leftarrow 0$\;
+	$n \leftarrow T.length()$ \;
+	$m \leftarrow P.length()$ \;
+	$LPS \leftarrow CalculateLPSArray(P)$ \;
+	$i \leftarrow 0$ \;
+	$j \leftarrow 0$ \;
+
+	\bigskip
+
+	\While{$j < n$}{
+		\If{$P[i] == T[j]$}{
 			$i \leftarrow i + 1$\;
+			$j \leftarrow j + 1$\;
 		}
-		\ElseIf{$length \neq 0$}{
-			$length \leftarrow LPS[length - 1]$\;
+		\If{$i == m$}{
+			\textbf{output} "Pattern found at index" $+ (j-i)$\;
+			$i \leftarrow LPS[i-1]$\;
 		}
+		\ElseIf{$j < n$ \textbf{and} $P[i] \neq T[j]$}{
+			\If{$i \neq 0$}{
+				$i \leftarrow LPS[i - 1]$\;}
 			\Else{
-			$LPS[i] \leftarrow 0$\;
-			$i \leftarrow i + 1$\;
+				$j \leftarrow j + 1$\;
 			}
-	}
-	\textbf{return} $LPS$
-	\caption{CalculateLPSArray}
+	}}
+	\caption{KMP Match}
 \end{algorithm}
@@
 
+By skipping the unecessary character comparisons, the algorithm proves to be much
+more efficient than the Naive approach. This is seen in its worst-case time complexity,
+which is $O(n + m)$ (best-case time complexity remains the same). As for the time complexities in the pre-processing and matching phases, they are $O(m)$ and $O(n)$ respectively
+
 \subsection{Rabin-Karp Algorithm}
 
+[12] The most similar out of the two to the Naive approach, the Rabin-Karp algorithm
+has a similar process of checking every substring for a match. Unlike the Naive approach
+however, this algorithm compares “hash values”. These are calculated using rolling hash
+functions, which allow for the removal and introduction of characters to the calculation,
+eliminating the need to recalculate the value entirely from scratch. To perform the hashing
+process on a substring, the following steps are carried out:
+
+\begin{question}[\bf{Rolling Hash Function}]
+\begin{enumerate}
+	\item The base $(b)$ and modulus $(p)$ values are chosen (usually prime numbers).
+	\item A hash value is initialised to 0 and the initial hash value of $P$ calculated (for each character in $P$, its contribution is added to the hash value as $c \cdot (b^{m-i-1}) \% p$.
+	\item The hash value for the first substring of length $m$ in $T$ is calculated.
+	\item Everytime $j$ is incremented, the contribution of the leftmost character is removed, the contribution of the rightmost character added.
+	\item Compare the text and pattern matches each time; if they match then it is a \textbf{potential match} (rolling function outputs can be the same for different inputs).
+To verify the match, a character match is performed.
+
+\end{enumerate}
+\end{question}
+
+The time complexity for the pre-processing phase (calculating $P$'s hash value) is $O(m)$.
+As for the time complexities in the matching phase, they are $O(m \cdot n)$ for the worst case
+scenario and $O(n + m)$ for the expected case. Although this algorithm maintains the
+simplicity of the Naive algorithm all the while improving its efficiency, it has a disadvantage that, depending on the specific $T$ case, may impact its efficiency -- a spurious
+hit. This refers to the case where a hash value match is made between $P$ and $T$ but the
+characters do not match, increasing the time complexity. This can however be minimized
+by implementing a robust hash function.
+
+The pseudocode for the algorithm is presented here below:
+
+\begin{center}
+\begin{singlespace}
+\begin{minipage}{0.75\linewidth}
+\begin{algorithm}[H]
+	$n \leftarrow T.length()$ \;
+	$m \leftarrow P.length()$ \;
+	$h \leftarrow 1$ \;
+	$hashT \leftarrow 0$ \;
+	$hashP \leftarrow 0$ \;
+
+	\bigskip
+
+	\For{$i \leftarrow 1$ \textbf{to} $m-1$}{
+		$h \leftarrow (h \cdot b) \% p$ \;
+	}
+
+	\bigskip
+
+	\For{$i \leftarrow 0$ \textbf{to} $m-1$}{
+		$hashP \leftarrow (b \cdot hashP + P[i]) \% p$ \;
+		$hashT \leftarrow (b \cdot hashT + T[i]) \% p$ \;
+	}
+
+	\bigskip
+
+	\For{$i \leftarrow 0$ \textbf{to} $n - m$}{
+		$match \leftarrow TRUE$ \;
+
+		\For{$j \leftarrow 0$ \textbf{to} $m - 1$}{
+			\If{$P[j] \neq T[i + j]$}{
+				$match \leftarrow FALSE$ \;
+			}
+		}
+
+		\If{$match == TRUE$}{}
+			\textbf{output} "Pattern found at index " $+ i$\;
+		\If{$i < n - m$}{
+			$hashT \leftarrow (b \cdot hashT + T[i]) + T[i + m] \% p$ \;
+			\If{$hashT < 0$}{
+				$hashT \leftarrow hashT + p$ \;
+			}
+		}
+	}
+\caption{Rabin Karp}
+\end{algorithm}
+\end{minipage}
+\end{singlespace}
+\end{center}
+
 \section{Experimental Methodology}
+
+In order to plan and carry out a methodology that will directly address the research
+question, the question must first be decomposed into specific key terms. These will aid
+in the decisions of variables, tools, and process.
+To re-iterate the question:
+\textbf{“How do different string matching algorithms perform across various application domains, and what factors contribute to their varying effectiveness?”}
+
+This can be broken down into three parts: measuring the performance of the mentioned
+string algorithms, applying these to different domains, and analyzing the results by making
+links back to the theory in order to understand the reasons behind their varying efficiency.
+The former two can be examined as part of the methodology, whereas the latter will be
+used as part of the analysis and conclusion.
 
@@
 
-% Numbered question, with an optional title
-\begin{question}[\itshape (with optional title)]
-	In congue risus leo, in gravida enim viverra id.
-Donec eros mauris, bibendum vel dui at, tempor commodo augue.
-In vel lobortis lacus.
-Nam ornare ullamcorper mauris vel molestie.
-Maecenas vehicula ornare turpis, vitae fringilla orci consectetur vel.
-Nam pulvinar justo nec neque egestas tristique.
-Donec ac dolor at libero congue varius sed vitae lectus.
-Donec et tristique nulla, sit amet scelerisque orci.
-Maecenas a vestibulum lectus, vitae gravida nulla.
-Proin eget volutpat orci.
-Morbi eu aliquet turpis.
-Vivamus molestie urna quis tempor tristique.
-Proin hendrerit sem nec tempor sollicitudin.
-\end{question}
-
 \end{document}

### 2023-10-22 paper/main.tex
these references really not be referencing

--- 2023-10-21 main.tex
@@
 
-For instance, multiple studies have been recently published performing various comparative analyses of new string matching algorithms [5], and their applicability to a wide range of domains such as biological sequences [6], quantum computing [7], and instrusion detection systems [8].
+For instance, multiple studies have been recently published performing various comparative analyses of new string matching algorithms [4], and their applicability to a wide range of domains such as biological sequences [5], quantum computing [6], and instrusion detection systems [7].
 These findings indicate the modern-day relevance and applicability of string matching algorithms and demonstrate its worthiness as a subject of investigation.
@@
 Similarly, this paper seeks to adopt an investigative style by examining \textbf{how different string matching algorithms perform across various application domains, and the factors that contribute to their varying effectiveness}.
-The choice of this research question is both relevant and justifiable, reflecting the persistent demand for evaluating and optimizing string matching algorithms across a range of applications.
+
+To formulate a methodology that will directly address this aim, the research question can be broken down into three parts: measuring the performance of the mentioned string algorithms, analyzing the results by making links back to the theory in order to the understand the reasons behind their varying efficiency, and linking these to different domains.
 
 To examine this subject, three popular string matching algorithms were programmed and tested on their ability to carry out three tasks from three different domains.
-They are then evaluated on their efficiency, and applicability.
+They are then evaluated on a set of criteria to determine their efficiency and applicability.
 To maintain focus on the research question, the reasoning and rationale behind all the decisions will be explained to demonstrate how they directly address the question.
+
+The choice of this research question is both relevant and justifiable, reflecting the persistent demand for evaluating and optimizing string matching algorithms across a range of applications.
 
@@
 	\item \textbf{Find occurences of a pre-defined pattern in a previously unseen dataset} \\
-	Carried out using finite automata models [4] (an idealized machine used to recognize
+	Carried out using finite automata models [2] (an idealized machine used to recognize
 	patterns in a given text; it accepts or rejects the input depending on whether the
@@
 
-[9] Also known as the “brute-force” approach, this algorithm compares the first indexes
+[8] Also known as the “brute-force” approach, this algorithm compares the first indexes
 of both $P$ and $T$. If $P_{i}$ equals $T_{j}$ then $i$ and $j$ are incremented and further compared. If
@@
 phase, the only time complexity taken into account is during its matching phase, which
-is expected to be $O(n \cdot m)$ [10]. The algorithm is better expressed in pseudocode:
+is expected to be $O(n \cdot m)$ [2]. The algorithm is better expressed in pseudocode:
 
@@
 
-[10] [11] This algorithm differs from the Naive approach by implementing an LPS table
+[2] [9] This algorithm differs from the Naive approach by implementing an LPS table
 as part of the pre-processing phase. Its purpose is to keep track of the comparisons made;
@@
 
-[12] The most similar out of the two to the Naive approach, the Rabin-Karp algorithm
+[10] The most similar out of the two to the Naive approach, the Rabin-Karp algorithm
 has a similar process of checking every substring for a match. Unlike the Naive approach
@@
 
-In order to plan and carry out a methodology that will directly address the research
-question, the question must first be decomposed into specific key terms. These will aid
-in the decisions of variables, tools, and process.
-To re-iterate the question:
-\textbf{“How do different string matching algorithms perform across various application domains, and what factors contribute to their varying effectiveness?”}
-
-This can be broken down into three parts: measuring the performance of the mentioned
-string algorithms, applying these to different domains, and analyzing the results by making
-links back to the theory in order to understand the reasons behind their varying efficiency.
-The former two can be examined as part of the methodology, whereas the latter will be
-used as part of the analysis and conclusion.
-
-\subsection{Research Question Decomposition}
-
 \subsection{Measuring Performance}
 
+To measure the detailed algorithms' performance, their mentioned pseudocode algorithms were programmed in $Python$ $3.12$. 
+Python was chosen due to it's wide array of third-party modules, two of which are used as part of the implementation: $Time$ and $Matplotlib$. 
+$Time$ is used to measure the algorithms' runtimes for each algorithm, and $Matplotlib$ is used to generate the graphical plots.
+Using their implementations, the following variables will be measured:
+
+\begin{enumerate}
+	\item \textbf{Dependent Variables} \\
+	\underline{Time (ms)} - The amount of time taken to search a pattern $P$ in a text $T$. \\
+	\underline{Number of Comparisons (pattern)} - The number of comparisons made between the pattern characters. \\
+	\underline{Number of Comparisons (text)} - The number of references made to the text (until all instances of the pattern are found).
+	\item \textbf{Control Variables} \\
+	\underline{Language} - Depending on whether the language employs a compiler or an interpetor, runtime speeds can differ.
+Moreover, the type of programming language (procedural, functional, etc.) can have an impact on how the code is run, further impacting runtime speed.\\
+	\underline{Pattern Length} - By controlling this factor, it is ensured that variations in number of comparisons and runtime are due to the algorithms themselves. This 
+\end{enumerate}
+
+The algorithms are then evaluated on their performance based on a set of constructed criteria:
+
+\begin{table}[!htbp]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+        \hline
+        Criteria & Testing \\
+        \hline
+        Time complexity & A \\
+        Space complexity & B \\
+        Simplicity & A \\
+        Applicability & B \\
+        \hline
+    \end{tabular}
+    \caption{Evaluation Criteria}
+\end{table}
+
 \subsection{Application to Domains}
+Plagiarism detection, DNA sequencing, Search Engine
 
 \section{Experimental Results Analysis}
+\subsection{Advantages and Disadvantages}
 
@@
 \section{References}
-
+\begin{itemize}
+	\item [1] eswitha_reddy. (2022, November 7). Applications of string matching algorithms. GeeksforGeeks. https://www.geeksforgeeks.org/applications-of-string-matching-algorithms/ 
+	\item [2] Gimel'farb, G. (2011, May 2). String matching algorithms - auckland. String Matching Algorithm. https://www.cs.auckland.ac.nz/courses/compsci369s1c/lectures/GG-notes/CS369-StringAlgs.pdf 
+	\item [3] harendrakumar123.
+(2023, May 8).
+Introduction to pattern searching - data structure and algorithm tutorial.
+GeeksforGeeks.
+https://www.geeksforgeeks.org/introduction-to-pattern-searching-data-structure-and-algorithm-tutorial/
+	\item [4] Gao, M., Huang, R., Mazumder, A.
+R., and Li, F.
+(2022).
+Comparisons of classic and quantum string matching algorithms*.
+Proceedings of the 4th International Conference on Advanced Information Science and System.
+https://doi.org/10.1145/3573834.3574498
+	\item [5] Muhammad Yusuf Muhammad, Mathias Fonkam, Salu George Thandekatu, Sandip Rakshit, and Rao Narasimha Vajjhala.
+(2023).
+COMPARATIVE ANALYSIS OF BIT-PARALLEL STRING PATTERN MATCHING ALGORITHMS FOR BIOLOGICAL SEQUENCES.
+Operational Research in Engineering Sciences: Theory and Applications, 6(1).
+Retrieved from https://oresta.org/menu-script/index.php/oresta/article/view/554
+	\item [6] Lecroq, T. (2023). Optimal-Hash Exact String Matching Algorithms. arXiv preprint arXiv:2303.05799. 
+	\item [7] K Azarudeen et al 2021 J. Phys.: Conf. Ser. 1916 012007 
+	\item [8] GeeksforGeeks. (2023c, October 20). Naive algorithm for pattern searching. https://www.geeksforgeeks.org/naive-algorithm-for-pattern-searching/?ref=lbp 
+	\item [9] GeeksforGeeks. (2023a, May 4). KMP algorithm for pattern searching. https://www.geeksforgeeks.org/kmp-algorithm-for-pattern-searching/?ref=lbp 
+	\item [10] GeeksforGeeks. (2023b, September 6). Rabin-Karp algorithm for pattern searching. https://www.geeksforgeeks.org/rabin-karp-algorithm-for-pattern-searching/?ref=lbp 
+\end{itemize}
 \end{document}

### 2023-10-23 paper/main.tex
???

@@
 
-\section{References}
-\begin{itemize}
-	\item [1] eswitha_reddy. (2022, November 7). Applications of string matching algorithms. GeeksforGeeks. https://www.geeksforgeeks.org/applications-of-string-matching-algorithms/ 
-	\item [2] Gimel'farb, G. (2011, May 2). String matching algorithms - auckland. String Matching Algorithm. https://www.cs.auckland.ac.nz/courses/compsci369s1c/lectures/GG-notes/CS369-StringAlgs.pdf 
-	\item [3] harendrakumar123.
-(2023, May 8).
-Introduction to pattern searching - data structure and algorithm tutorial.
-GeeksforGeeks.
-https://www.geeksforgeeks.org/introduction-to-pattern-searching-data-structure-and-algorithm-tutorial/
-	\item [4] Gao, M., Huang, R., Mazumder, A.
-R., and Li, F.
-(2022).
-Comparisons of classic and quantum string matching algorithms*.
-Proceedings of the 4th International Conference on Advanced Information Science and System.
-https://doi.org/10.1145/3573834.3574498
-	\item [5] Muhammad Yusuf Muhammad, Mathias Fonkam, Salu George Thandekatu, Sandip Rakshit, and Rao Narasimha Vajjhala.
-(2023).
-COMPARATIVE ANALYSIS OF BIT-PARALLEL STRING PATTERN MATCHING ALGORITHMS FOR BIOLOGICAL SEQUENCES.
-Operational Research in Engineering Sciences: Theory and Applications, 6(1).
-Retrieved from https://oresta.org/menu-script/index.php/oresta/article/view/554
-	\item [6] Lecroq, T. (2023). Optimal-Hash Exact String Matching Algorithms. arXiv preprint arXiv:2303.05799. 
-	\item [7] K Azarudeen et al 2021 J. Phys.: Conf. Ser. 1916 012007 
-	\item [8] GeeksforGeeks. (2023c, October 20). Naive algorithm for pattern searching. https://www.geeksforgeeks.org/naive-algorithm-for-pattern-searching/?ref=lbp 
-	\item [9] GeeksforGeeks. (2023a, May 4). KMP algorithm for pattern searching. https://www.geeksforgeeks.org/kmp-algorithm-for-pattern-searching/?ref=lbp 
-	\item [10] GeeksforGeeks. (2023b, September 6). Rabin-Karp algorithm for pattern searching. https://www.geeksforgeeks.org/rabin-karp-algorithm-for-pattern-searching/?ref=lbp 
-\end{itemize}
+\bibliographystyle{plain}
+reference style
+\bibliography{references}
 \end{document}

### 2023-11-03 paper/main.tex
a misplaced underscore caused all this fuss

@@
 
-For instance, multiple studies have been recently published performing various comparative analyses of new string matching algorithms [4], and their applicability to a wide range of domains such as biological sequences [5], quantum computing [6], and instrusion detection systems [7].
+For instance, multiple studies have been recently published performing various comparative analyses of new string matching algorithms \parencite{4}, and their applicability to a wide range of domains such as biological sequences \parencite{5}, quantum computing \parencite{6}, and instrusion detection systems \parencite{7}.
 These findings indicate the modern-day relevance and applicability of string matching algorithms and demonstrate its worthiness as a subject of investigation.
@@
 \subsection{Topic Overview}
-String matching algorithms (often used interchangeably with string or pattern searching
+\parencite{3} String matching algorithms (often used interchangeably with string or pattern searching
 algorithms) are a subset of string algorithms. The term is composed of three parts:
 “string”, “matching”, and “algorithm”. Strings refer to an abstract data type consisting
-1
 of a sequence of characters. Matching relates to it's function to identify specific patterns
@@
 sequence, a text ($T$). Within string matching problems, there exists two general variants
-[2]:
+\parencite{2}:
 
@@
 	\item \textbf{Find occurences of a pre-defined pattern in a previously unseen dataset} \\
-	Carried out using finite automata models [2] (an idealized machine used to recognize
+	Carried out using finite automata models \parencite{2} (an idealized machine used to recognize
 	patterns in a given text; it accepts or rejects the input depending on whether the
@@
 
-Linking into the mentioned problem variants, these algorithms can be further classified into two categories [1]: exact, and approximate string matching algorithms. As
+Linking into the mentioned problem variants, these algorithms can be further classified into two categories \parencite{1}: exact, and approximate string matching algorithms. As
 its name suggests, the former refers to finding occurences of a pattern that match it to
@@
 
-[8] Also known as the “brute-force” approach, this algorithm compares the first indexes
+\parencite{8} Also known as the “brute-force” approach, this algorithm compares the first indexes
 of both $P$ and $T$. If $P_{i}$ equals $T_{j}$ then $i$ and $j$ are incremented and further compared. If
@@
 phase, the only time complexity taken into account is during its matching phase, which
-is expected to be $O(n \cdot m)$ [2]. The algorithm is better expressed in pseudocode:
+is expected to be $O(n \cdot m)$ \parencite{2}. The algorithm is better expressed in pseudocode:
 
@@
 
-[2] [9] This algorithm differs from the Naive approach by implementing an LPS table
+\parencite{2} \parencite{9} This algorithm differs from the Naive approach by implementing an LPS table
 as part of the pre-processing phase. Its purpose is to keep track of the comparisons made;
@@
 
-[10] The most similar out of the two to the Naive approach, the Rabin-Karp algorithm
+\parencite{10} The most similar out of the two to the Naive approach, the Rabin-Karp algorithm
 has a similar process of checking every substring for a match. Unlike the Naive approach
@@
 	\item The base $(b)$ and modulus $(p)$ values are chosen (usually prime numbers).
-	\item A hash value is initialised to 0 and the initial hash value of $P$ calculated (for each character in $P$, its contribution is added to the hash value as $c \cdot (b^{m-i-1}) \% p$.
+	\item A hash value is initialised to 0 and the initial hash value of $P$ calculated (for each character in $P$, its contribution is added to the hash value as $c \cdot (b^{m-i-1}) \% p$).
 	\item The hash value for the first substring of length $m$ in $T$ is calculated.
@@
 
-\bibliographystyle{plain}
-reference style
-\bibliography{references}
+\printbibliography
 \end{document}

### 2023-11-04 paper/main.tex
khalasna section 3

@@
 
+A practical example is also illustrated:
+
+\begin{figure}[H]
+	\includegraphics[scale=0.6]{naive_figure}
+	\centering
+	\caption{Illustrated Naive \parencite{11}}
+\end{figure}
+
+As can be seen, both indexes for the pattern (111) and the text (1011101110) begin at 0 and their first characters are compared.
+As they match, the indexes are incremented for both P and T and their respective characters matched.
+As they do not, the index for the pattern is reset to 0 and the text's index incremented.
+In the depicted example, this is repeated twice more before a match is found -- everytime the index of the pattern increases, it matches with the increasing text index.
+
 The best case scenario of this process is when $P_{i=0}$ is not present in $T$, yielding an
@@
 
+A practical example is also illustrated:
+
+\begin{figure}[H]
+	\includegraphics[scale=0.7]{kmp_figure}
+	\centering
+	\caption{Illustrated KMP \parencite{12}}
+\end{figure}
+
+Firstly, the pattern is pre-processed to create an LPS table.
+This works by iterating through each character of the pattern, and determining its earliest occurrence within it.
+For example, beginning with “k”, it is its first instance in the pattern and so there is no other earliest occurrence, so it is registered in the LPS table as -1, to indicate that there are not any.
+This repeats for the next 2 characters.
+Upon reaching index 3 with “k”, it is noticed that its earliest instance now exists and is found at index 0, and so it is registered in the LPS table as so.
+This process continues for the rest of the pattern.
+Afterwards, the “longest proper prefix which is also a suffix” is found by taking the longest sub-list of consecutive LPS values.
+In this case it would be indexes 6 to 1 (kmpkmp).
+This array is then used as part of the string matching to skip the unnecessary comparisons (in the example, since it is known that the prefix equals the suffix, when kmpkmd is reached, the next 7 characters can be skipped, since based on the LPS table they are known not to match).
+
 By skipping the unecessary character comparisons, the algorithm proves to be much
 more efficient than the Naive approach. This is seen in its worst-case time complexity,
-which is $O(n + m)$ (best-case time complexity remains the same). As for the time complexities in the pre-processing and matching phases, they are $O(m)$ and $O(n)$ respectively
+which is $O(n + m)$ (best-case time complexity remains the same). As for the time complexities in the pre-processing and matching phases, they are $O(m)$ and $O(n)$ respectively.
 
@@
 
+A practical example is also illustrated:
+
+\begin{figure}
+    \centering
+    \subfloat[\centering Pattern Hash Code]{{\includegraphics[scale=0.55]{rabin_karp_figure1} }}
+    \qquad
+    \subfloat[\centering Comparison With Text]{{\includegraphics[scale=0.55]{rabin_karp_figure2} }}
+    \caption{Illustrated Rabin Karp \parencite{13}}
+\end{figure}
+
+To aid with comprehension, the rolling hash function used to calculate hash values is replaced with a simplified hashing function: each character is converted to its numerical position within the alphabet (e.g.
+a = 1, b = 2).
+Since it is known that the pattern length is $m$ = 3, the hash values of groups of 3 characters are calculated from the text each time.
+Using the predefined assigned hash values for the characters, the pattern's hashcode is calculated to yield 4.
+This means that for each sub-group within the text that is examined, its hashcode should yield 4 to be deemed a potential match.
+In the example, the hashcode for the first group examined (aaa) is calculated (3).
+Since they do not match, the second sub-group is checked (aaa).
+This continues up until the end of the text, where no match is found.
+
 \section{Experimental Methodology}
@@
 To measure the detailed algorithms' performance, their mentioned pseudocode algorithms were programmed in $Python$ $3.12$. 
-Python was chosen due to it's wide array of third-party modules, two of which are used as part of the implementation: $Time$ and $Matplotlib$. 
-$Time$ is used to measure the algorithms' runtimes for each algorithm, and $Matplotlib$ is used to generate the graphical plots.
+Python was chosen due to it's wide array of third-party modules, three of which are used as part of the implementation: $time$, $matplotlib$ and $cProfile$. 
+$time$ is used to measure the algorithms' runtimes for each algorithm, $matplotlib$ is used to generate the graphical plots, and $cProfile$ is used to calculate the time and space-complexities of the programs.
+An experimental methodology was chosen as their is limited secondary data available due to the high specificity of the task.
+Furthermore, this methodology provides increased control over variable manipulation.
 Using their implementations, the following variables will be measured:
@@
 	\item \textbf{Dependent Variables} \\
-	\underline{Time (ms)} - The amount of time taken to search a pattern $P$ in a text $T$. \\
-	\underline{Number of Comparisons (pattern)} - The number of comparisons made between the pattern characters. \\
-	\underline{Number of Comparisons (text)} - The number of references made to the text (until all instances of the pattern are found).
+	\underline{Pre-processing runtime (ms)} - The amount of time taken to prepare the data prior to matching.\\
+	\underline{Matching runtime (ms)} - The amount of time taken to search a pattern $P$ in a text $T$.\\
+	\underline{Total number of comparisons} - The total number of references made to the text (until all instances of the pattern are found) \\
+	\underline{Total number of comparisons with unmatching characters} - The total number of references made to the text for characters that do not match (until all instances of the pattern are found).
 	\item \textbf{Control Variables} \\
@@
 Moreover, the type of programming language (procedural, functional, etc.) can have an impact on how the code is run, further impacting runtime speed.\\
-	\underline{Pattern Length} - By controlling this factor, it is ensured that variations in number of comparisons and runtime are due to the algorithms themselves. This 
+	\underline{Pattern} - More specifically pattern length and occurrence within the text.
+By controlling this factor, it is ensured that variations in number of comparisons and runtime are due to the algorithms themselves.
 \end{enumerate}
@@
     \centering
-    \begin{tabular}{|c|c|c|c|}
+    \begin{tabular}{|c|p{12cm}|}
         \hline
-        Criteria & Testing \\
+        \textbf{Criteria} & \textbf{Testing} \\
         \hline
-        Time complexity & A \\
-        Space complexity & B \\
-        Simplicity & A \\
-        Applicability & B \\
+        Time complexity & Using the $Python$ $cProfile$ library. \\[0.25cm]
+        Space complexity & Using the $Python$ $memory\_profiler$ library. \\[0.25cm]
+        Simplicity & Subjective qualitative judgement. \\[0.25cm]
+        Applicability & More specifically \textbf{pattern length} and \textbf{occurrence} within the text.
+By controlling this factor, it is ensured that variations in number of comparisons and runtime are due to the algorithms themselves.
+\\
         \hline
@@
 \end{table}
-
-\subsection{Application to Domains}
-Plagiarism detection, DNA sequencing, Search Engine
+\pagebreak
+\subsection{Dataset}
+Two pieces of primary data were collected for the experiment, the text and the patterns to match.
+The same text (3000 character long English text) was used across tests for all three algorithms.
+As for the patterns, 30 were obtained (generated pseudorandomly from text) each with a length of $m$ from 1 to 20 to yield a total of 600 data points.
+The high data yield will allow for more reliable and justified judgements on trends to be made.
+The choice of 30 patterns was made as it was found to be an appropriate quantity for a text of this length.
+As for the 20 lengths of $m$, this was done as it would provide a wide range of results to observe a trend without compromising on runtime.
+To account for edge cases, one pattern not found within the text was included.
 

### 2023-11-04 paper/main.tex
cant believe its done

@@
 
-\date{\textbf{Words}: not enough} % University, school and/or department name(s) and a date
+\date{\textbf{Words}: 3514} % University, school and/or department name(s) and a date
 
@@
 To measure the detailed algorithms' performance, their mentioned pseudocode algorithms were programmed in $Python$ $3.12$. 
-Python was chosen due to it's wide array of third-party modules, three of which are used as part of the implementation: $time$, $matplotlib$ and $cProfile$. 
-$time$ is used to measure the algorithms' runtimes for each algorithm, $matplotlib$ is used to generate the graphical plots, and $cProfile$ is used to calculate the time and space-complexities of the programs.
+Python was chosen due to it's wide array of third-party modules, three of which are used as part of the implementation: $timeit$, $matplotlib$, and $random$. 
+$timeit$ is used to measure the algorithms' runtimes for each algorithm, $matplotlib$ is used to generate the graphical plots, and $random$ is used to generate the patterns.
 An experimental methodology was chosen as their is limited secondary data available due to the high specificity of the task.
@@
 By controlling this factor, it is ensured that variations in number of comparisons and runtime are due to the algorithms themselves.
+\\
+	\underline{Prime Number} - An additional input is required for Rabin-Karp's algorithm - a prime number (q). For all trials q will equal to 101 to limit its' effect on the results.
 \end{enumerate}
@@
         \hline
-        Time complexity & Using the $Python$ $cProfile$ library. \\[0.25cm]
-        Space complexity & Using the $Python$ $memory\_profiler$ library. \\[0.25cm]
+        Time complexity & Analyzing program structure. \\[0.25cm]
+        Space complexity & Analyzing program structure. \\[0.25cm]
         Simplicity & Subjective qualitative judgement. \\[0.25cm]
@@
 
-\section{Experimental Results Analysis}
-\subsection{Advantages and Disadvantages}
+\subsection{Programs}
+\subsubsection{Pseudorandom Pattern Generator}
+
+\begin{singlespace}
+\begin{python}
+import random
+
+patterns = []
+
+for pattern_num in range(30):
+	for pattern_length in range(1,21):
+		random_initial_position = random.randint(0, 2999)
+		new_pattern = text[random_initial_position : random_initial_position + pattern_length]
+		patterns.append(new_pattern)
+\end{python}
+\end{singlespace}
+
+\subsubsection{Conducting Matches}
+Total and unmatching matches were calculated within the actual algorithm functions.
+
+\begin{singlespace}
+\begin{python}
+import timeit
+
+patterns = sorted(patterns, key=len)
+q = 101
+
+kmp_preprocessing_runtimes = []
+rabin_karp_preprocessing_runtimes = []
+
+naive_runtimes = []
+kmp_runtimes = []
+rabin_karp_runtimes = []
+
+total_matches_naive = []
+total_matches_kmp = []
+total_matches_rabin_karp = []
+
+unmatching_matches_naive = []
+unmatching_matches_kmp = []
+unmatching_matches_rabin_karp = []
+
+for pattern in patterns:
+	# Preprocessing runtimes
+	start = timeit.default_timer()
+	computeLPSArray(pattern, len(pattern), [0]*len(pattern))
+	stop = timeit.default_timer()
+	runtime = stop - start
+	kmp_preprocessing_runtimes.append(runtime)
+
+	start = timeit.default_timer()
+	rolling_hash(pattern)
+	stop = timeit.default_timer()
+	runtime = stop - start
+	rabin_karp_preprocessing_runtimes.append(runtime)
+
+	# Matching runtimes
+	start = timeit.default_timer()
+	kmp(pattern, text)
+	stop = timeit.default_timer()
+	runtime = stop - start
+	kmp_runtimes.append(runtime)
+
+	start = timeit.default_timer()
+	naive(pattern, text)
+	stop = timeit.default_timer()
+	runtime = stop - start
+	naive_runtimes.append(runtime)
+
+	start = timeit.default_timer()
+	rabin_karp(pattern, text, q)
+	stop = timeit.default_timer()
+	runtime = stop - start
+	kmp_runtimes.append(runtime)
+
+\end{python}
+\end{singlespace}
+
+\subsubsection{Generating Graphical Plots}
+
+Pattern length vs runtimes:
+\begin{python}
+\begin{singlespace}
+import matplotlib.pyplot as plt
+
+pattern_lengths = [len(i) for i in patterns]
+
+plt.figure(figsize=(8, 6))
+plt.scatter(pattern_lengths, naive_runtimes, marker='.', label="Naive")
+plt.scatter(pattern_lengths, rabin_karp_runtimes, marker='.', label="Rabin Karp")
+plt.scatter(pattern_lengths, kmp_runtimes, marker='.', label="KMP")
+
+plt.title('Pattern Length vs Runtimes')
+plt.xlabel('Pattern Length')
+plt.ylabel('Runtime (ms)')
+
+plt.legend()
+plt.grid()
+plt.show()
+\begin{singlespace}
+\end{python}
+
+Barchart for preprocessing runtimes:
+\begin{python}
+\begin{singlespace}
+avg_preprocessing_rabin_karp = sum(rabin_karp_preprocessing_runtimes) / 600
+avg_preprocessing_kmp = sum(kmp_preprocessing_runtimes) / 600
+
+algorithms = ['Rabin-Karp', 'KMP']
+preprocessing_runtimes = [avg_preprocessing_rabin_karp, avg_preprocessing_kmp]
+
+fig, ax = plt.subplots()
+bar_container = ax.bar(algorithms, preprocessing_runtimes, color=['y', 'g'])
+ax.set(ylabel='runtime (ms)', title='Average Preprocessing Runtimes for Rabin-Karp and KMP')
+ax.bar_label(bar_container, fmt=lambda x: f'{x}')
+\begin{singlespace}
+\end{python}
+
+Pattern length vs total number of comparisons:
+\begin{python}
+\begin{singlespace}
+plt.figure(figsize=(8, 6))
+plt.scatter(pattern_lengths, total_matches_naive, marker='.', label="Naive")
+plt.scatter(pattern_lengths, total_matches_rabin_karp, marker='.', label="Rabin Karp")
+plt.scatter(pattern_lengths, total_matches_kmp, marker='.', label="KMP")
+
+plt.title('Pattern Length vs Total Number of Comparisons')
+plt.xlabel('Pattern Length')
+plt.ylabel('Total Number of Comparisons')
+
+plt.legend()
+plt.grid()
+plt.show()
+\begin{singlespace}
+\end{python}
+
+Pattern length vs number of unmatching comparisons:
+\begin{python}
+\begin{singlespace}
+plt.figure(figsize=(8, 6))
+plt.scatter(pattern_lengths, unmatching_matches_naive, marker='.', label="Naive")
+plt.scatter(pattern_lengths, unmatching_matches_rabin_karp, marker='.', label="Rabin Karp")
+plt.scatter(pattern_lengths, unmatching_matches_kmp, marker='.', label="KMP")
+
+plt.title('Pattern Length vs Number of Unmatching Comparisons')
+plt.xlabel('Pattern Length')
+plt.ylabel('Number of Unmatching Comparisons')
+
+plt.legend()
+plt.grid()
+plt.show()
+\begin{singlespace}
+\end{python}
+
+\section{Experimental Results}
+\subsection{Graphical Presentation}
+Since the number of datapoints is too high to be presented as a table, only graphical representations will be presented.
+These allows for a more intuitive and visual view of the results which in turn aids in identifying patterns and trends.
+As demonstrated with the programs, these produced the four following graphs which are presented below in their most appropriate presentation forms:
+
+\begin{tikzpicture}
+\matrix[matrix of nodes]{
+\includegraphics[scale=0.4]{results1} & \includegraphics[scale=0.5]{results2} \\
+};
+\end{tikzpicture}
+
+\begin{tikzpicture}
+	\matrix[matrix of nodes]{
+	\includegraphics[scale=0.4]{results3} & \includegraphics[scale=0.4]{results4} \\
+	};
+\end{tikzpicture}
+
+Each of the graphs above (except the barchart) depict the three algorithms' performance based on the examined dependent variables.
+The plots are depicted as scatter plots as no observable trend was yet inferred.
+It should also be noticed that their is no third bar to the barchart as the Naive algorithm does not have a preprocessing stage.
+
+\subsection{Data Analysis}
+This section will be structured by algorithm; in each sub-section, the algorithm's performance depicted on each of the four plots will be examined, as well as its trend and how it can be explained.
+Afterwards, it will be judged against the criteria and be considered with the examined performance to make an overall judgement that will be applied to the three domains: DNA sequencing, plagiarism detection and search engines.
+
+\subsubsection{Naive Algorithm}
+
+Firstly, it should be noticed across the runtimes that all three algorithms seem to spike in runtime around the 7.5 length region.
+This may be an anomaly that might have occurred due to the specific characteristic of that particular pseudorandomly generated pattern.
+Out of the three, the Naive algorithm performed the best, with the lowest average runtime.
+Considering the simplicity of it, this performance is unexpected, and might be attributed to a the dataset - this can be examined further by using a wider set of data to confirm its unusual performance.
+This unexpected trend continues throughout the third plot, with it having an average total number of comparisons lying close to 3000, which remains stable throughout, demonstrating a linear trend with a gradient of 0.
+In the number of unmatching comparisons, it performs marginally better than KMP, however in comparison to Rabin Karp it performs much worse, and this can be attributed to its brute force method.
+
+In comparison with the criteria, its time and space complexity are $O(n-m+1)$ and $O(1)$ respectively.
+This will be put into perspective with the other algorithms at the end of the analyses.
+Its simplicity out of the three is already known to be the most.
+As for its application to domains, it was demonstrated to perform well with smaller datasets, however the areas of applications generally concern themselves with massive databases, hence it would not be appropriate to use this algorithm on any of these applications.
+
+\subsubsection{KMP Algorithm}
+
+For the matching runtimes, KMP is relatively in the middle compared to the two others, with its trend following the same similar spikes.
+Its preprocessing time did not follow the same trend, with it performing 52.5\% worse than Rabin Karp.
+Its total number of comparisons was also significantly higher than the other algorithms, sitting at an average close to 6000.
+The final plot also depicts the same trend, with its average number of unmatching comparisons being marginally above 3000.
+These results can be explained in the opposite way to Naive - KMP’s performance improves in comparison to other algorithms as the pattern lengths increase, however with small datasets it is not the most efficient.
+
+This is further justified in its time and space complexities which are both $O(m)$ for the preprocessing stage, and $O(n)$ with $O(1)$ for the matching stages.
+Its simplicity can be examined in two areas: the LPS table and the matching.
+The LPS table is relatively understandable and can be easily visualised.
+The latter however is more complicated, as it is more difficult to imagine how the LPS table fits onto the text to skip comparisons.
+Its notable characteristic of the LPS table, aswell as its suggested improved performance with large datasets renders it a more appropriate method to use with the mentioned domains.
+
+\subsubsection{Rabin Karp Algorithm}
+
+For this last algorithm, it is first seen that it spends the most amount of time in the matching stage, with it having the worst runtime.
+Its average preprocessing runtime is much improved in comparison to KMP’s and its matching one, which can be attributed to the low time cost of the hashing function.
+In the last two plots, it can be seen to excel in terms of the number comparisons.
+The average total lies around 3000 which is close to Naive, and it has a negligible number of unmatching comparisons, which is the most ideal.
+
+Overall, Rabin Karp represents the ideal compromise between performance and the other evaluation criteria.
+It has a time and space complexity of $O(m)$ and $O(1)$ in the preprocessing stage, and an average of $O(m+n)$ and $O(1)$ in the matching stage.
+As was demonstrated, it works well with smaller datasets, and its algorithm design suggests it would be the same with larger ones.
+The only realy difficulty with its comprehension is the hash function, however this can be visualised for better understanding.
+Its performance however may vary depending on characteristics of text, which will vary the number of spurious hits obtained.
+However, the general results demonstrate stability, going in hand with reliability.
+This links to the domains, as its demonstrated characteristics are ideal for applications areas of this genre.
 
@@
 
+Linking the examined information together, the evaluated criteria for each algorithm is presented here below:
+\pagebreak
+\begin{table}[!htbp]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+        \hline
+        \textbf{Algorithm} & \textbf{Naive} & \textbf{KMP} & \textbf{Rabin Karp} \\
+        \hline
+        \textbf{Preprocessing Time Complexity} & N/A & $O(m)$ & $O(m)$ \\[0.25cm]
+		\textbf{Preprocessing Space Complexity} & N/A & $O(m)$ & $O(1)$ \\[0.25cm]
+        \textbf{Matching Time Complexity} & $O(n-m+1)$ & $O(n)$ & $O(m+n)$\\[0.25cm]
+        \textbf{Matching Space Complexity} & $O(1)$ & $O(1)$ & $O(1)$\\[0.25cm]
+        \textbf{Simplicity} & 3 & 2 & 2 \\[0.25cm]
+        \textbf{Applicability} & 1 & 2 & 3 \\[0.25cm]
+        \hline
+    \end{tabular}
+    \caption{Evaluated Criteria}
+\end{table}
+
+Overall, taking into consideration all the criteria points, Rabin Karp is the best performer across all these factors, followed by KMP and Naive.
+This directly addresses and answers the research question, as various tests were conducted on the algorithms to determine performance, the obtained results were graphed and analysed by linking back to the theory to examine the underlying factors for their varying performances.
+Finally, these were linked to the three domains, to understand how and whether they should be applied to these areas.
+
+\section{Further Research Opportunities}
+One research opportunity concerns the q variable (prime number) that was controlled in the experimental methodology. 
+It's exact influence on the results was not determined, so a suggestion for a further investigation would be exploring how varying the magnitude of q affects the 4 dependent variables.
+Another research opportunity would be investigating more string matching algorithms and evaluating them, as having a broader view of a wider variety of algorithms can help in making better judgements as to which should be chosen for which specific purpose or domain.
+
 \printbibliography
